Fast Sorting on Modern Computers

### 2005-08-18 docs/tech_report/heap.tex
tocuhed up, and added mini-conclusion

The relationship between this number and $H_N-1$ is relatively straightforward.
$H_N-1$ represents the cumulative number of changes in the minimum. Over a long
array, this approximates the number of branch mispredictions, as almost every
branch will not be taken, and the predictor will always predict not-taken. The
graph shows us the rate of correct predictions, and each point is calculated
using a seperate branch predictor. As a result, we expect $1-y = \frac{1}{x+1}$,
where $x$ and $y$ are the cartesian coordinates of each point on the graph.
$1-y$ is the number of mispredictions from the graph, while $\frac{1}{x+1}$ is
the increase of $H_N$ for step $N$.

When the array is short, as in this example, the branch predictor has too much
feedback to be as accurate as $H_N$. For $N=2$, we would approximate a 33\%
misprediction ratio using $H_N$, but we measure 39\%. The approximated and
actual ratios become closer as $N$ increases, as we would expect, and for $N=7$,
we approximate 12.5\% and measure 12.7\%.

>>>>

The relationship between this number and $H_N-1$ is relatively straightforward.
$H_N-1$ represents the cumulative number of changes in the minimum. Over a long
array, this approximates the number of branch mispredictions, as almost every
branch will not be taken, and the predictor will always predict not-taken.

Meanwhile, Figure \ref{memory-tuned heapsort curve} shows us the rate of correct
predictions, and each point is calculated using a seperate branch predictor. As
a result, we expect $1-y = \frac{1}{x+1}$, where $x$ and $y$ are the cartesian
coordinates of each point on the graph.  $1-y$ is the number of mispredictions
from the graph, while $\frac{1}{x+1}$ is the increase in $H_N$ for step $N$.

When the array is short, as in this example, the branch predictor has too much
feedback to be close to $H_N$. For $N=2$, we would approximate a 33\%
misprediction ratio using $H_N$, but we measure 39\%. The approximated and
actual ratios become closer as $N$ increases, as we would expect, and for $N=7$,
we approximate 12.5\% and measure 12.7\%. We conclude that initial suggestion is
correct: while the branch prediction ratio of finding the minimum is very close
to $H_N-1$, the relationship is less accurate for very short arrays.
